Predictive modeling with cross validation

### 2017-08-23 model fitting/cross_validation.Rmd
added splines with psplines in coxph and rcs in cph fits

```{r, echo = FALSE}
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
str(splitPlan)
```

@@

```{r, echo = FALSE}
# write a function to set up variables for this training data

train1 <- x[splitPlan[[1]]$train, ]

first <- coxph(Surv(time_until_answer, answered) ~ category + as.factor(new_user) + contain_unanswered + title_questionmark + text_length + text_contain_punct + as.factor(num_freq_tags) + as.factor(n_tags) + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1)
AIC(first, k = 2) #65294.56

# backwards step-wise selection with selectCox function
# converting to factors since function doesn't work with as.factor()
train1$new_user <- as.factor(train1$new_user)
train1$num_freq_tags <- as.factor(train1$num_freq_tags)
train1$n_tags <- as.factor(train1$n_tags)

model1 <- pec::selectCox(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + text_length + text_contain_punct + num_freq_tags + n_tags + contain_answered + newline_ratio + text_all_lower + update + greeting + capital_text + prior_effort + gratitude + ampm + n_images + weekday + device_length + title_beginwh, data = train1, rule = "aic")
# results
results1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + contain_answered + text_all_lower + update + ampm + device_length, data = train1)
AIC(results1, k = 2) #65285.49
summary(results1)

# backward/forward step-wise selection with stepAIC function from MASS package
model2 <- MASS::stepAIC(first, direction = "both", k = 2)
# results
results2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
AIC(results2, k = 2) # 65277.47
summary(results2)
```

### Adding interaction terms

* working with model from backward/forward stepwise selection

```{r, echo = FALSE}
# adding title_questionmark*title_beginwh
model2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh, data = train1)
AIC(model2, k = 2) # 65274.49
oshitar::compare_nested(model2, results2)

# adding new_user*update
model2_1 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*update, data = train1)
AIC(model2_1, k = 2) # 65272.55
compare_nested(model2_1, results2)

# adding new_user*ampm 
model2_2 <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_user*ampm, data = train1)
AIC(model2_2, k = 2) # 65271.84
oshitar::compare_nested(model2_2, results2)

# all signficant interaction terms 
model_i <- coxph(Surv(time_until_answer, answered) ~ category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm, data = train1)
AIC(model_i, k = 2) # 65263.35
```

##### recoding category variable

* group all apple products together
    + use str_detect to search for ipad, ipod, apple watch 
    + group with iPhones and Macs 
* recode left over Phones to Android/Other Phone
* group household + appliance as "Home"
* group car and truck + vehicle as "Vehicle"
* set a rule: any category with less than 100 questions gets grouped with "Other"

```{r, echo = FALSE}
train1$new_category <- as.character(train1$category)

# grouping apple products together
apple_terms <- c("apple", "ipod", "ipad")
train1$apple <- str_detect(str_to_lower(train1$device), pattern = START %R% or1(apple_terms) %R% SPC)
train1$new_category[train1$apple == TRUE | train1$subcategory == "iPhone" | train1$category == "Mac"] <- "Apple Product"

# renaming left over phones 
train1$new_category[train1$new_category == "Phone"] <- "Android/Other Phone"

# merge household and appliance into "Home"
train1$new_category[train1$new_category == "Appliance" | train1$new_category == "Household"] <- "Home"

# merging Car and Truck with Vehicle 
train1$new_category[train1$new_category == "Car and Truck" | train1$new_category == "Vehicle"] <- "Vehicle"

# if there are less than 100 questions in a category, group them with Other
counts <- train1 %>%
  group_by(new_category) %>%
  summarise(n = n())
for (i in which(counts$n <= 100)) {
  train1$new_category[train1$new_category == counts$new_category[i]] <- "Other"
}
table(train1$new_category)

#===================================================

model_new <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh, data = train1)
AIC(model_new, k = 2) #64999.87
summary(model_new)

#new_cateogry*new_user
model_new1 <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + new_category*new_user, data = train1)
AIC(model_new1, k = 2) # 64994.49
compare_nested(model_new1, model_new)

# model with ALL interactions
# model with new_category
model_full <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1)
AIC(model_full, k = 2) # 64978.87
summary(model_full)
```

@@

* Martingale residuals
    + plot for each continuous predictor 
    + assess adequacy of functional form of predictors, or suggest a potential form 
* Deviance residuals
    + check for outliers identify questions poorly predicted by the model 
    + one plot, examine questions with |residuals| > 2.5
* Schoenfeld residuals
    + one plot for each predictor 
    + if loess curve is flat, proportional hazard assumption is not violated, doesn't depend on time. Distinct pattern indicates violation of this assumption
    + **from the plots:** new_user, title_questionmark, num_freq_tags (1), ampm (Morning, Night), weekday (Thursday, Saturday), new_user*AMPM (morning, night) may violate PH assumption 
* Score residuals
    + check for influential observations. ID quesitons who's predictor values highly effect parameter estimates
    + plot for each predictor 
* **figure out how to identify certain points on ggplots**
* statified on new_category, AIC dropped drastically. But this means that I can't compare the different groups in new_category 
    + Concordance statistic and rsquare dropped

@@

### Checking multicolliniearity

```{r, echo = FALSE}
rms::vif()
```

@@

* model not stratified on new_category has higher R2, higher Dxy than model stratified on new_category
* survConcordance: 
    + Concordance is defined as Pr(agreement) for any two randomly chosen observations, where in this case agreement means that the observation with the shorter survival time of the two also has the larger risk score. The predictor (or risk score) will often be the result of a Cox model or other regression
    + some of the pairs are incomparable. For instance a pair of times (5+, 8), the first being a censored value. We do not know whether the first survival time is greater than or less than the second
    + observations that are comparable, pairs may also be tied on survival time (but only if both are uncensored) or on the predictor. The final concondance is (agree + tied/2)/(agree + disagree + tied)
    +

```{r}
# working with final model (stratified on new_category) 
train_predict <- predict(object = strat_model, type = "risk", se.fit = TRUE)
train1$predictions <- train_predict[[1]]

(performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.115
AIC(performance, k = 2) # 65781.26

survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train1) # Concordance = 0.5573537

Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions, data = train1)

#=============================================

# working with full_model (not stratified on new_category)
train_predict2 <- predict(object = model_full, type = "risk", se.fit = TRUE)
train1$predictions2 <- train_predict2[[1]]
(performance2 <- rms::cph(Surv(time_until_answer, answered) ~ predictions2, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.270

survConcordance(Surv(time_until_answer, answered) ~ predictions2, data = train1) # Concordance = 0.634903

Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions2, outx = TRUE, data = train1)

#=============================================

# working with strat_model1 (stratified on new_user)
train_predict3 <- predict(object = strat_model1, type = "risk", se.fit = TRUE)
train1$predictions3 <- train_predict3[[1]]
(performance3 <- rms::cph(Surv(time_until_answer, answered) ~ predictions3, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.244

survConcordance(Surv(time_until_answer, answered) ~ predictions3, data = train1) # Concordance = 0.6221597

Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions3, data = train1)

#=============================================

# working with strat_model2 (stratified on ampm)
train_predict4 <- predict(object = strat_model2, type = "risk", se.fit = TRUE)
train1$predictions4 <- train_predict4[[1]]
(performance4 <- rms::cph(Surv(time_until_answer, answered) ~ predictions4, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE)) # Dxy 0.258

survConcordance(Surv(time_until_answer, answered) ~ predictions4, data = train1) # Concordance = 0.6289692

Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions4, data = train1)
```

### working with the rms package for cross validation

```{r, echo = FALSE}
(cox <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))

options(scipen=999)
(cv <- rms::validate(cox, method = "crossvalidation", B = 10, dxy = TRUE, pr = TRUE))

# for calibrate function, had to add in surv = TRUE and time.inc = a constant (time at which to estimate survival probabilities)
cox1 <- rms::cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE, surv=TRUE, time.inc=1.5)

calibrate <- rms::calibrate(cox1, method = "crossvalidation", B = 10, pr = TRUE)
```

@@

  # building model on training data set
  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = train)

  # performance metrics for training data 
  train[["predictions"]] <- predict(model, type = "risk")
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2), 
                              R2 = round(metric$stats[8],2), 
                              Dxy = round(metric$stats[9],2), 
                              AIC = stats::AIC(metric, k = 2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

@@

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = round(metric1$stats[3],2), 
                             pval = round(metric1$stats[5],2), 
                             R2 = round(metric1$stats[8],2), 
                             Dxy = round(metric1$stats[9],2), 
                             AIC = stats::AIC(metric1, k = 2), 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

@@

#=============================================
test1 <- oshitar::variable_setup(x[splitPlan[[1]]$app, ])
(iteration1 <- crossvalidate(train1, test1))

#=============================================
train2 <- oshitar::variable_setup(x[splitPlan[[2]]$train, ])
test2 <- oshitar::variable_setup(x[splitPlan[[2]]$app, ])
(iteration2 <- crossvalidate(train2, test2))

#=============================================
train3 <- oshitar::variable_setup(x[splitPlan[[3]]$train, ])
test3 <- oshitar::variable_setup(x[splitPlan[[3]]$app, ])
test3$num_freq_tags <- as.character(test3$num_freq_tags)
test3$num_freq_tags[test3$num_freq_tags == "4"] <- "3"
(iteration3 <- crossvalidate(train3, test3))
# make this more reproducible!!! rule: if a factors level has less than 3 observations in it, merge it with the nearest level

#=============================================
train4 <- oshitar::variable_setup(x[splitPlan[[4]]$train, ])
test4 <- oshitar::variable_setup(x[splitPlan[[4]]$app, ])
(iteration4 <- crossvalidate(train4, test4))

#=============================================
train5 <- oshitar::variable_setup(x[splitPlan[[5]]$train, ])
test5 <- oshitar::variable_setup(x[splitPlan[[5]]$app, ])
(iteration5 <- crossvalidate(train5, test5))

@@

@@

final <- coxph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + title_questionmark + num_freq_tags + contain_answered + text_all_lower + update + ampm + weekday + device_length + title_beginwh + title_questionmark*title_beginwh + new_user*update + new_user*ampm + new_category*new_user, data = x)
summary(final)
AIC(final, k = 2) # 83051.61

>>>>

```{r, echo = FALSE}
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)
str(splitPlan)

train1 <- x[splitPlan[[1]]$train, ]
```

@@

```{r, echo = FALSE}
fit <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + log10(text_length) + title_questionmark + title_beginwh + sqrt(newline_ratio) + sqrt(avg_tag_score) + text_contain_punct + text_all_lower + update + greeting + as.factor(n_tags) + gratitude + prior_effort + ampm + n_images + weekday, data = train1)

model <- MASS::stepAIC(fit, direction = "both", k = 2)
#results of stepAIC (but keeping contain_answered)
results <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday, data = train1)
summary(results)
AIC(results, k = 2) # 64965.89

# adding in spline on device_length
model_spline <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC"), data = train1)
AIC(model_spline, k = 2) # 64907.21

# adding in spline on text_length
model_spline1 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC"), data = train1)
AIC(model_spline1, k = 2) # 64894.01

# adding in spline on avg_tag_length
model_spline2 <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train1)
summary(model_spline2)
AIC(model_spline2, k = 2) # 64848.5

anova(model_spline2)

#=====================================================
# adding interaction between title_questionmark + title_beginwh (probably leave out)
# probably leave interactions out, don't do much for the model

resultse <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + title_questionmark + title_beginwh + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC") + title_questionmark*title_beginwh, data = train1)
summary(resultse)
AIC(resultse, k = 2) # 64843
```

# using rcs (restricted cubic spline) in rms package 
* fit knots at quantiles of the predictor 
* recommended in Regression Modeling Strategies to have 5 knots for large data sets 
```{r}
unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.725, 0.95)))

library(rms)
model <- cph(Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + rcs(device_length, unname(quantile(train1$device_length, c(0.05, 0.275, 0.5, 0.65, 0.95)))), data = train1)
AIC(model_spline, k = 2) # 64907.21
model
```

@@

* Martingale residuals
    + plot for each continuous predictor 
    + assess adequacy of functional form of predictors, or suggest a potential form 
* Deviance residuals
    + check for outliers identify questions poorly predicted by the model 
    + one plot, examine questions with |residuals| > 2.5
* Schoenfeld residuals
    + one plot for each predictor 
    + if loess curve is flat, proportional hazard assumption is not violated, doesn't depend on time. Distinct pattern indicates violation of this assumption
    + **from the plots:** new_user, title_questionmark, num_freq_tags (1), ampm (Morning, Night), weekday (Thursday, Saturday), new_user*AMPM (morning, night) may violate PH assumption 
* Score residuals
    + check for influential observations. ID quesitons who's predictor values highly effect parameter estimates
    + plot for each predictor 
* **figure out how to identify certain points on ggplots**

@@

@@

* survConcordance: 
    + Concordance is defined as Pr(agreement) for any two randomly chosen observations, where in this case agreement means that the observation with the shorter survival time of the two also has the larger risk score. The predictor (or risk score) will often be the result of a Cox model or other regression
    + some of the pairs are incomparable. For instance a pair of times (5+, 8), the first being a censored value. We do not know whether the first survival time is greater than or less than the second
    + observations that are comparable, pairs may also be tied on survival time (but only if both are uncensored) or on the predictor. The final concondance is (agree + tied/2)/(agree + disagree + tied)

```{r}
# working with model_spline2 (model with all splines)
train1$predictions <- predict(object = model_spline2, type = "risk") # should I predict "lp" instead of "risk"
(performance <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train1, x = TRUE, y = TRUE, se.fit = TRUE, residuals = TRUE))

survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train1) # Concordance = 0.6382697
Hmisc::rcorrcens(Surv(time_until_answer, answered) ~ predictions, data = train1)

```

@@

  # building model on training data set
  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train)

  # performance metrics for training data 
  train[["predictions"]] <- predict(model, type = "risk")
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2), 
                              Dxy = round(metric$stats[9],2), 
                              AIC = stats::AIC(metric, k = 2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

@@

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = round(metric1$stats[3],2), 
                             pval = round(metric1$stats[5],2), 
                             Dxy = round(metric1$stats[9],2), 
                             AIC = stats::AIC(metric1, k = 2), 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

@@

#=============================================
test1 <- x[splitPlan[[1]]$app, ]
iteration1 <- crossvalidate(train1, test1)

#=============================================
train2 <- x[splitPlan[[2]]$train, ]
test2 <- x[splitPlan[[2]]$app, ]
iteration2 <- crossvalidate(train2, test2)

#=============================================
train3 <- x[splitPlan[[3]]$train, ]
test3 <- x[splitPlan[[3]]$app, ]
iteration3 <- crossvalidate(train3, test3)

#=============================================
train4 <- x[splitPlan[[4]]$train, ]
test4 <- x[splitPlan[[4]]$app, ]
iteration4 <- crossvalidate(train4, test4)

#=============================================
train5 <- x[splitPlan[[5]]$train, ]
test5 <- x[splitPlan[[5]]$app, ]
iteration5 <- crossvalidate(train5, test5)

@@

```{r}
# without pspline on text_length (if take out pspline on text_length, pvalue for fifth iteration goes back down to 0 (from 0.53))
crossvalidate1 <- function(train, test) {

  # building model on training data set
  model <- survival::coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = train)

  # performance metrics for training data 
  train[["predictions"]] <- predict(model, type = "risk")
  metric <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = train)
  train_metrics <- data.frame(HR = exp(metric$coefficients), 
                              LR = round(metric$stats[3],2), 
                              pval = round(metric$stats[5],2), 
                              Dxy = round(metric$stats[9],2), 
                              AIC = stats::AIC(metric, k = 2), 
                              Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = train)$concordance)

  # computing performance metrics 
  metric1 <- rms::cph(Surv(time_until_answer, answered) ~ predictions, data = test)
  test_metrics <- data.frame(HR = exp(metric1$coefficients), 
                             LR = round(metric1$stats[3],2), 
                             pval = round(metric1$stats[5],2), 
                             Dxy = round(metric1$stats[9],2), 
                             AIC = stats::AIC(metric1, k = 2), 
                             Concordance = survConcordance(Surv(time_until_answer, answered) ~ predictions, data = test)$concordance)

i1 <- crossvalidate1(train1, test1)
i2 <- crossvalidate1(train2, test2)
i3 <- crossvalidate1(train3, test3)
i4 <- crossvalidate1(train4, test4)
i5 <- crossvalidate1(train5, test5)

i1; i2; i3; i4; i5
```

@@

final <- coxph(Surv(time_until_answer, answered) ~ new_category + as.factor(new_user) + contain_unanswered + contain_answered + title_questionmark + sqrt(avg_tag_score) + text_all_lower + update + prior_effort + ampm + weekday + pspline(device_length, df = 0, method = "AIC") + pspline(text_length, df = 0, method = "AIC") + pspline(avg_tag_length, df = 0, method = "AIC"), data = x)
summary(final)
AIC(final, k = 2) # 83051.61
